---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Holly Gustavsen"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```

If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?

```{r}
covid_data_long |> 
  filter(count_type == "Cases", race == "Total") |> 
  ggplot(aes(x = date, y = count, color = state)) + geom_line()
```

In this plot, the number of cases vs the date is displayed with each state being a different color. By color alone it is difficult to tell which state is which though. Some trends I noticed are that the states with the most cases started having more cases earlier and that pretty much all the states start to spike around December. 

2. Are there any conclusions you can draw?

From the graph you can tell which states have the most cases however it would be hard to draw conclusions based off this graph alone when there are other factors affecting the data. Furthermore because the graph shows all 50 states it is hard to tell which color is actually which state. 

3. What were you not able to do due to not having the R knowledge?

I wanted to plot average proportion of cases by race vs date but because each race was its own column instead of being one column and each state had its own proportion I wasn't sure how to.  

4. What other data would be useful to better understand this data?

I think gendr and/or age would be helpful for understanding and drawing more conclusions about the data.
